Exploring Design Space for Differentially Private Bayesian Inference

### 2018-12-27 ICML2019/main.tex
update abstract and conclusion

In this work, we explore the design space for differentially private bayesian inference, by considering different metrics and different algorithms we design a mechanism. 
We focus on two discrete models, the Beta-Binomial and the
Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
Our mechanism can be understood as a version of  the exponential mechanism
where the noise is calibrated to the smooth sensitivity of the
utility function, rather than to its global sensitivity. In our
setting, the utility function is the probability distance we want to
use to measure accuracy. To show the usefulness of this mechanism we
show an experimental analysis comparing it with mechanisms based on
the Laplace mechanism.
\end{abstract}
 % TODO: replace with your keywords

@@

\section{Preliminaries}
\label{sec_background}

@@

\section{Problem Statement}
\label{sec_moti}
We are interested in exploring mechanisms for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (Beta, Dirichlet distribution) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{sec_mechs}.

@@

\subsubsection{using $\ell_1$ norm metric}
 Adding noise to the posterior distribution parameters directly, through Laplace mechanism with post-processing, $\lapmech(\bysinfer, \dataobs)$, producing an output:

 \[
\lapmech(\bysinfer, \dataobs) = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \] 
 where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
 \begin{equation*}
 \begin{split}
 & \lapmech(\bysinfer, \dataobs) = \\
 & \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \end{split}
 \end{equation*}
 where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model. $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.

@@

 \[
 \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \]
 where $Y \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
 \[
 \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \]
where $Y_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.

@@

In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference. \cite{dimitrakakis2014robust}, \cite{zhang2016differential}, \cite{zheng2015differential} and \cite{wang2015privacy}. 2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}. 3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy. The third topic where our work focus on is still very new.

\section{Conclusion}
From what we have seen in the previous sections we can obtain some preliminary conclusions. That is, the probabiliy measure approach outperforms the $\ell_1$-norm approach in the following cases:

\begin{enumerate}
	\item  $\hexpmech$ outperforms the baseline approach but not the improved one, for priors with small parameters.
  	\item When the prior parameters increase $\hexpmech$ is comparable with the improved baseline approach.
\end{enumerate}

>>>>

In this work, we explore the design space for differentially private bayesian inference, by considering different metrics and different algorithms we design a mechanism. 
We focus on two discrete models, the Beta-Binomial and the
Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
For different algorithms, we explore three main mechanisms based on the Laplace algorithm family and exponential algorithm family.
For different metrics, we apply them by calibrating noise to the sensitivity of that utility function, where the utility function is the probability metric we want to
use to measure accuracy. To show the usefulness of these mechanisms we
show an experimental analysis comparing their performance.
\end{abstract}
 % TODO: replace with your keywords

@@

\section{Problem Setting}

\subsection{Preliminaries}
\label{sec_background}

@@

\subsection{Technical Problem Statement}
\label{subsec_problem}
We are interested in exploring mechanisms for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (Beta, Dirichlet distribution) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{sec_mechs}.

@@

\subsubsection{using $\ell_1$ norm metric}
 Adding noise to the posterior distribution parameters directly, through Laplace mechanism with post-processing, $\lapmech(\bysinfer, \dataobs)$, producing an output:
$$
\begin{array}{rcl}
& \lapmech(\bysinfer, \dataobs) \\
& = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
\end{array} 
$$
 where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
$$
\begin{array}{rcl}
 & \lapmech(\bysinfer, \dataobs) = \\
 & \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \\
 & \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
\end{array} 
$$
 where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model. $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.

@@

$$
\begin{array}{rcl}
& \ilapmech(\bysinfer, \dataobs) \\
& = \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
\end{array} 
$$
 where $Y \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
$$
\begin{array}{rcl}
 & \ilapmech(\bysinfer, \dataobs) = \\
 & \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \\
 & \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
\end{array} 
$$
where $Y_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.

@@

In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference. \cite{dimitrakakis2014robust}, \cite{zhang2016differential}, \cite{zheng2015differential} and \cite{wang2015privacy}. 2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}. 3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy. The third topic where our work focus on is still very new. moreover, their design spaces are more specific to the $\ell_1$ norm and Laplace mechanism. That's why we explore different metrics and different algorithms over the design space.

\section{Conclusion}
From what we have seen in the previous sections we can obtain following conclusions. We explored the design space of the mechanisms for differentially privacy Bayesian inference, by considering different metrics and different algorithms.
\begin{itemize}
  \item The accuracy can change a lot when considering different metrics and using different sensitivity values.
  \item Different algorithms have different performance w.r.t. different aspect. From the experimental results, Laplace mechanism family have a good efficiency and accuracy when using $\ell_1$ norm metric. But exponential mechanism family can be a good application when considering different metrics.
\end{itemize}
